\tool

### 2017-12-10 paper/paper.tex
Notes for methodology

%\begin{table}
%	\centering
%	\caption{Evaluation Projects}
%	\begin{tabular}{|l|l|l|c|}
%		\hline
%		\textbf{Project} & \textbf{Java Files} & \textbf{LOC} & \textbf{Pull Requests} \\
%		\hline
%		spring-boot\footnote{https://github.com/spring-projects/spring-boot.git} &  &  & \\
%		\hline
%		dubbo\footnote{https://github.com/alibaba/dubbo.git} &  &  & \\
%		\hline
%		guava\footnote{https://github.com/google/guava.git}  &  &  & \\
%		\hline
%		retrofit\footnote{https://github.com/square/retrofit.git}  &  &  & \\
%		\hline
%		rocketmq\footnote{https://github.com/apache/rocketmq.git}  &  &  & \\
%		\hline
%		\end{tabular}
%	\begin{tablenotes}
%        \item[1] Details on projects used for study including GitHub repository name, number of Java files, lines of Java code, and total pull requests.
%    \end{tablenotes}
%	\label{tools}
%\end{table}
%

@@

We divided our study into two segments to address each research question:

\subsubsection{RQ1}

Last 100 pull requests on repositories...

\subsubsection{RQ2}

@@

No false positives... \\

>>>>

\subsection{Participants}

Are we collecting any information on the developers?

@@

We designed our research study to address each  of our research questions.

\pseudosubsection{RQ1}

Quantitative (track number of recs over time)

\pseudosubsection{RQ2}

Qualitative (survey)

\subsection{Data Analysis}

\pseudosubsection{RQ1}

Redirected pull requests to me to prevent false positives

\pseudosubsection{RQ2}

@@
